Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-15 document/ms.tex
some notes about papers to cite

\begin{abstract}
Although no true extra-solar Earth analog is known, hundreds of planets have
been found around Sun-like stars that are either Earth-sized but on shorter
periods, or else on year-long orbits but somewhat bigger than Earth.
These populations ought to permit a (possibly highly uncertain) extrapolated
measurement of the probability or rate at which Sun-like stars host true Earth
analogs.
Here we present a general probabilistic framework for making justified
inferences about the occurrence rate of exoplanets taking into account survey
completeness \emph{and observational uncertainties}.
We demonstrate that our method produces lower variance estimates than the
standard inverse-detection-efficiency weighting procedure.
When applied to an existing catalog of small planet candidates around G dwarfs
(Petigura \etal\ 2013), our method confirms previous measurements of a
flattening radius distribution near Earth's radius.
One output of our models is fully marginalized estimates---marginalizing out
observational uncertainties and all distribution parameters---of the rate
density of true Earth analogs, expressed as a number of planets per star per
natural logarithmic interval of period and radius, evaluated at the properties
of Earth.
The rate density we infer is an extrapolation; it depends strongly on the
permitted flexibility of the distribution model, but it tends to come out
at around ten percent, with large uncertainty.
\end{abstract}

@@

@@

@@

@@

@@

>>>>

\begin{abstract}

An impressive number of exoplanets have been discovered and it is of great
scientific interest to study what we can say about the exoplanet occurence
rate function given these discoveries.
Every catalog is censored by non-trivial selection effects and detection
efficiencies, and the measurements of the system properties (period, radius,
\etc) are noisy.
We present a general hierarchical probabilistic framework for making justified
inferences about the occurrence rate of exoplanets taking into account survey
completeness \emph{and observational uncertainties}.
By applying our method to synthetic catalogs, we demonstrate that it produces
more accurate estimates of the underlying occurence rate than the standard
inverse-detection-efficiency weighting procedure.
When applied to an existing catalog of small planet candidates around G dwarfs
(Petigura \etal\ 2013), our method confirms previous measurements of a
flattening radius distribution near Earth's radius.
Although no true extra-solar Earth analog is known, hundreds of planets have
been found around Sun-like stars that are either Earth-sized but on shorter
periods, or else on year-long orbits but somewhat larger.
Under strong assumptions, it has been shown that these populations permit an
uncertain extrapolated estimate of the probability or rate at which Sun-like
stars host true Earth analogs.
We relax these assumptions by modeling the occurence rate as a
multidimensional Gaussian process and find that the rate density of Earth
analogs is about two percent with large uncertainty.

\end{abstract}

@@

CITATIONS:
\begin{itemize}
\item
\citet{fressin-fp} --- simultaneous occurence rate and false positive rate
\item
\citet{morton} --- false positive rate
\item
\citet{morton-swift} --- KDE estimator for radius distribution of cool KOIs
\item
\citet{howard} --- inv-det-eff for short-period candidates around Sun-like
stars
\item
\citet{dressing} --- inv-det-eff for cool KOIs
\item
\citet{dong} --- semi-analytic completeness, likelihood function-ish,
turn-over at small radii, non-separability
\item
\citet{tabachnik} ---- Poisson likelihood
\item
\citet{tremaine} --- statistics of multis
\item
\citet{youdin} --- Poisson likelihood
\item
\citet{catanzarite} --- extrapolation to Eta-Earth assuming complete
\item
\citet{traub} --- extrapolation to Eta-Earth assuming complete
\end{itemize}

@@

\bibitem[Catanzarite \& Shao(2011)]{catanzarite}
Catanzarite, J., \& Shao, M.\ 2011, \apj, 738, 151 (\arxiv{1103.1443})

@@

\bibitem[Fressin \etal(2013)]{fressin-fp}
Fressin, F., Torres, G., Charbonneau, D., \etal\ 2013, \apj, 766, 81
(\arxiv{1301.0842})

@@

\bibitem[Morton \& Johnson(2011)]{morton}
Morton, T.~D., \& Johnson, J.~A.\ 2011, \apj, 738, 170 (\arxiv{1101.5630})

\bibitem[Morton \& Swift(2013)]{morton-swift}
Morton, T.~D., \& Swift, J.~J.\ 2013, \arxiv{1303.3013}

@@

\bibitem[Traub(2012)]{traub}
Traub, W.~A.\ 2012, \apj, 745, 20 (\arxiv{1109.4682})
